Untitled

### 2020-03-19 Rmd/World_Map_Breeding_Systems.Rmd
Maps, and code for species names

 "Monoecy" = "#984EA3","Dioecy" = "orange")) +labs(title = "Breeding systems",subtitle = "",
  caption = "",fill = NULL) + theme(legend.position = c(0.215, 0.010),legend.justification = c(1, 0),
  axis.ticks = element_blank(),legend.key.size = unit(0.2, "cm")) +

>>>>

 "Monoecy" = "#984EA3","Dioecy" = "orange")) +labs(title = "Breeding system",subtitle = "",
  caption = "",fill = NULL) + theme(legend.position = c(0.15, 0.010),legend.justification = c(1, 0),legend.text=element_text(size=5),
  axis.ticks = element_blank(),legend.key.size = unit(0.16, "cm")) +

### 2020-03-19 Rmd/World_Map_Life_Form.Rmd
Maps, and code for species names

---
title: "Untitled"
output:
  pdf_document: default
  html_document: default
---
```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE}

#Load Libraries
library(readxl)
library(ggplot2)
library(dbplyr)
library(scatterpie)
library(reshape2)
# READ LONG FORMAT DATA

setwd("~/R_Projects/Reproductive Traits")

@@

#READ TRAIT DATA IN ORDER TO MERGE
data <- read.csv("Data/Data_processing/all.csv", stringsAsFactors = F)
data <- data[,c(1,4,6,7,8,22,27)]
levels(as.factor(data$Breeding_system))
#Filter data for columns of interest
data_filtered <- subset(data, Info_level=="flower"|Info_level=="capitulum"|Info_level=="inflorescence"|Info_level=="NA")
#Rename column to merge
colnames(data_filtered)[1] <- "Plant_species"
#Convert to factor 
data_filtered <- as.data.frame(data_filtered, stringsAsFactors = TRUE)

@@

#Group breeding system per metaweb or web
all_summary_compatibility_system <- dcast(all_species_per_network,Id~Compatibility,value.var = "Compatibility")

#Cleaning NA and one unfinished network
all_summary_compatibility_system <- all_summary_compatibility_system[,c(1,5:8)]

all_summary_compatibility_system$partially_self_compatible <- as.numeric(all_summary_compatibility_system$partially_self_compatible) + as.numeric(all_summary_compatibility_system$self_compatible_self_incompatible) 
all_summary_compatibility_system <- all_summary_compatibility_system[ , -4]
#Removing ".csv" from the Id to megere with coordinates
all_summary_compatibility_system$Id <- gsub("\\..*","",all_summary_compatibility_system$Id)

@@

#Merge coordinates and data 
data_merged <- merge(metadata_sub, all_summary_compatibility_system)

@@

data_merged_sub_ord[,c(3,4,7:9)] <- sapply(data_merged_sub_ord[,c(3,4,7:9)],as.numeric)
str(data_merged_sub_ord)

#network size fix

@@

  geom_map(map=world, aes(map_id=region), fill="white", color="grey", size=0.35) +

@@

 data = data_merged_sub_ord, cols = colnames(data_merged_sub_ord[,c(7:9)]),alpha=.8)+ 
  scale_fill_manual(breaks = colnames(data_merged_sub_ord[,c(7:9)]),
 labels = c("Partially self compatible", "Self compatible", "Self incompatible"),values = c("partially_self_compatible" = "#4DAF4A","self_compatible" = "#984EA3","self_incompatible" = "orange")) +labs(title = "Compatibility systems",subtitle = "", caption = "",fill = NULL) + theme(legend.position = c(0.18, 0.010),legend.justification = c(1, 0),legend.text=element_text(size=5),
  axis.ticks = element_blank(),legend.key.size = unit(0.16, "cm")) +

>>>>

---
title: "Untitled"
output:
  pdf_document: default
  html_document: default
---
```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE}
#WORLDPLOT WITH LIFE FORM

#Load Libraries
library(readxl)
library(ggplot2)
library(dbplyr)
library(scatterpie)
library(reshape2)
# READ LONG FORMAT DATA
setwd("~/R_Projects/Reproductive Traits")

@@

#READ TRAIT DATA IN ORDER TO MERGE
data <- read.csv("Data/Data_processing/all.csv", stringsAsFactors = F)
data <- data[,c(1,4,6,7,8,51,27)]
levels(as.factor(data$Breeding_system))
#Filter data for columns of interest
data_filtered <- subset(data, Info_level=="flower"|Info_level=="capitulum"|Info_level=="inflorescence"|Info_level=="NA")
#Rename column to merge
colnames(data_filtered)[1] <- "Plant_species"
#Convert to factor 
data_filtered <- as.data.frame(data_filtered, stringsAsFactors = TRUE)

@@

#Group breeding system per metaweb or web
all_summary_life_form <- dcast(all_species_per_network,Id~life_form,value.var = "life_form")
#Cleaning NA and one unfinished network
all_summary_life_form <- all_summary_life_form[-c(6,30),-c(6)]
#Removing ".csv" from the Id to megere with coordinates
all_summary_life_form$Id <- gsub("\\..*","",all_summary_life_form$Id)

@@

#Merge coordinates and data 
data_merged <- merge(metadata_sub, all_summary_life_form)

@@

data_merged_sub_ord[,c(3,4,7:10)] <- sapply(data_merged_sub_ord[,c(3,4,7:10)],as.numeric)
str(data_merged_sub_ord)

@@

  geom_map(map=world, aes(map_id=region), fill="white", color="black") +

@@

                     data = data_merged_sub_ord, cols = colnames(data_merged_sub_ord[,c(7:10)]),alpha=.8)+ 
  scale_fill_manual(breaks = colnames(data_merged_sub_ord[,c(7:10)]),
                    labels = c("Herb", "Shrub", "Tree", "Vine"),values = c("herb" = "#4DAF4A",
                                                                           "shrub" = "#984EA3","tree" = "orange", "vine" = "lightblue")) +labs(title = "Life form",subtitle = "",
                                                                                                                                               caption = "",fill = NULL) + theme(legend.position = c(0.12, 0.009),legend.justification = c(1, 0),
                                                                                                                                                                                 axis.ticks = element_blank(),legend.key.size = unit(0.2, "cm")) +

### 2020-03-19 Rmd/World_Plots_Panel.Rmd
Maps, and code for species names

---
title: ""
output:
  pdf_document: default
  html_document: default
---
```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE}
#WORLDPLOT WITH BREEDING SYSTEMS

#Load Libraries
library(readxl)
library(ggplot2)
library(dbplyr)
library(scatterpie)
library(reshape2)
# READ LONG FORMAT DATA
setwd("~/R_Projects/Reproductive Traits")
Long_format_metawebs <- readRDS("Data/RData/Long_format_metawebs.RData")

@@

p <- ggplot(world, aes(long, lat)) +

@@

  coord_quickmap()+ylab("Latitude")+ xlab("Longitude")+coord_equal() + coord_sf( ylim = c(-60, 100), expand = FALSE)
p +  geom_scatterpie(aes(x=longitude, y=latitude,group=Id), 

@@

  caption = "",fill = NULL) + theme(legend.position = c(0.15, 0.010),legend.justification = c(1, 0),legend.text=element_text(size=5),

@@

>>>>

---
title: "Untitled"
output:
  pdf_document: default
  html_document: default
---
```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10,fig.width=40,fig.align = 'center'}
#WORLDPLOT WITH BREEDING SYSTEMS

#Load Libraries
library(readxl)
library(ggplot2)
library(dbplyr)
library(scatterpie)
library(reshape2)
library(effsize)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(cowplot)
library(gridExtra)
library(egg)
library(magrittr)
library(multipanelfigure)
library(grid)
# READ LONG FORMAT DATA
setwd("~/R_Projects/Reproductive Traits")
Long_format_metawebs <- readRDS("Data/RData/Long_format_metawebs.RData")

@@

p1 <- ggplot(world, aes(long, lat)) +

@@

  coord_quickmap()+ylab("Latitude")+ xlab("Longitude")+coord_equal() + coord_sf( ylim = c(-60, 100), expand = FALSE) +  geom_scatterpie(aes(x=longitude, y=latitude,group=Id), 

@@

  caption = "",fill = NULL) + theme(legend.position = c(0.15, 0.010),legend.justification = c(1, 0),legend.text=element_text(size=5),legend.key.size = unit(0.16, "cm")) +

#Load Libraries
library(readxl)
library(ggplot2)
library(dbplyr)
library(scatterpie)
library(reshape2)
# READ LONG FORMAT DATA

setwd("~/R_Projects/Reproductive Traits")

Long_format_metawebs <- readRDS("Data/RData/Long_format_metawebs.RData")

#READ TRAIT DATA IN ORDER TO MERGE
data <- read.csv("Data/Data_processing/all.csv", stringsAsFactors = F)
data <- data[,c(1,4,6,7,8,22,27)]
levels(as.factor(data$Breeding_system))
#Filter data for columns of interest
data_filtered <- subset(data, Info_level=="flower"|Info_level=="capitulum"|Info_level=="inflorescence"|Info_level=="NA")
#Rename column to merge
colnames(data_filtered)[1] <- "Plant_species"
#Convert to factor 
data_filtered <- as.data.frame(data_filtered, stringsAsFactors = TRUE)

#Group breeding system per metaweb or web
all_summary_compatibility_system <- dcast(all_species_per_network,Id~Compatibility,value.var = "Compatibility")

#Cleaning NA and one unfinished network
all_summary_compatibility_system <- all_summary_compatibility_system[,c(1,5:8)]

all_summary_compatibility_system$partially_self_compatible <- as.numeric(all_summary_compatibility_system$partially_self_compatible) + as.numeric(all_summary_compatibility_system$self_compatible_self_incompatible) 
all_summary_compatibility_system <- all_summary_compatibility_system[ , -4]
#Removing ".csv" from the Id to megere with coordinates
all_summary_compatibility_system$Id <- gsub("\\..*","",all_summary_compatibility_system$Id)

#Merge coordinates and data 
data_merged <- merge(metadata_sub, all_summary_compatibility_system)

data_merged$Id <- as.factor(data_merged$Id)
str(data_merged)

#I have done this in other code for other reasons
#I'm going to maintain it
data_merged_sub <- data_merged
#Plot data
world <- map_data('world')

data_merged_sub_ord[,c(3,4,7:9)] <- sapply(data_merged_sub_ord[,c(3,4,7:9)],as.numeric)
str(data_merged_sub_ord)

p2 <- ggplot(world, aes(long, lat)) +
  coord_quickmap()+ylab("Latitude")+ xlab("Longitude")+coord_equal() + coord_sf( ylim = c(-60, 100), expand = FALSE) +  geom_scatterpie(aes(x=longitude, y=latitude,group=Id), 
 labels = c("Partially self compatible", "Self compatible", "Self incompatible"),values = c("partially_self_compatible" = "#4DAF4A","self_compatible" = "#984EA3","self_incompatible" = "orange")) +labs(title = "Compatibility system",subtitle = "", caption = "",fill = NULL) + theme(legend.position = c(0.18, 0.010),legend.justification = c(1, 0),legend.text=element_text(size=5),

@@

#Load Libraries
library(readxl)
library(ggplot2)
library(dbplyr)
library(scatterpie)
library(reshape2)
# READ LONG FORMAT DATA
setwd("~/R_Projects/Reproductive Traits")

Long_format_metawebs <- readRDS("Data/RData/Long_format_metawebs.RData")

#READ TRAIT DATA IN ORDER TO MERGE
data <- read.csv("Data/Data_processing/all.csv", stringsAsFactors = F)
data <- data[,c(1,4,6,7,8,51,27)]
levels(as.factor(data$Breeding_system))
#Filter data for columns of interest
data_filtered <- subset(data, Info_level=="flower"|Info_level=="capitulum"|Info_level=="inflorescence"|Info_level=="NA")
#Rename column to merge
colnames(data_filtered)[1] <- "Plant_species"
#Convert to factor 
data_filtered <- as.data.frame(data_filtered, stringsAsFactors = TRUE)

#Group breeding system per metaweb or web
all_summary_life_form <- dcast(all_species_per_network,Id~life_form,value.var = "life_form")
#Cleaning NA and one unfinished network
all_summary_life_form <- all_summary_life_form[-c(6,30),-c(6)]
#Removing ".csv" from the Id to megere with coordinates
all_summary_life_form$Id <- gsub("\\..*","",all_summary_life_form$Id)

#Merge coordinates and data 
data_merged <- merge(metadata_sub, all_summary_life_form)

data_merged$Id <- as.factor(data_merged$Id)
str(data_merged)

#I have done this in other code for other reasons
#I'm going to maintain it
data_merged_sub <- data_merged
#Plot data
world <- map_data('world')

data_merged_sub_ord[,c(3,4,7:10)] <- sapply(data_merged_sub_ord[,c(3,4,7:10)],as.numeric)
str(data_merged_sub_ord)

p3 <- ggplot(world, aes(long, lat)) +
  geom_map(map=world, aes(map_id=region), fill="white", color="grey") +
  coord_quickmap()+ylab("Latitude")+ xlab("Longitude")+coord_equal() + coord_sf( ylim = c(-60, 100), expand = FALSE) +  geom_scatterpie(aes(x=longitude, y=latitude,group=Id), 
                     data = data_merged_sub_ord, cols = colnames(data_merged_sub_ord[,c(7:10)]),alpha=.8)+ 
  scale_fill_manual(breaks = colnames(data_merged_sub_ord[,c(7:10)]),
                    labels = c("Herb", "Shrub", "Tree", "Vine"),values = c("herb" = "#4DAF4A",
                                                                           "shrub" = "#984EA3","tree" = "orange", "vine" = "lightblue")) +labs(title = "Life form",subtitle = "",
                                                                                                                                               caption = "",fill = NULL) + theme(legend.position = c(0.12, 0.009),legend.justification = c(1, 0),
                                                                                                                                                                                 axis.ticks = element_blank(),legend.key.size = unit(0.2, "cm")) +

grid.arrange(p1, p2, p3, nrow=3)

 #grid.draw(arrangeGrob(ggplotGrob(p1),ggplotGrob(p2),nrow=2))
#mylegend
 dev.off()
